Towards End-user Web Scraping For Customization

### 2021-02-14 paper.tex
Added references to commercial scraping tools

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they wrote their scraping code in order to edit
and re-run it. In web customization, Vegemite \citep{lin2009}, a system
for end-user programming of mashups, reported that participants of its
user study thought ``it was confusing to use one technique to create the
initial table, and another technique to add information to a new
column.'' This hints at the need for a unified environment and a unified
workflow.

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-51} which does not support providing new demonstrations to
extend or repair the scraping code. In Vegemite \citep{lin2009}, a web
automation program created through demonstration can only be edited by
editing the text-based representation of the program.

@@

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Its interface does not provide
\emph{full} live feedback about its generalizations or the values to be
scrapped until all the demonstrations have been provided and the
generated program has been run. If run on a website it has encountered
before, Rousillon makes all the previously determined generalizations
visible to the user by color-coding the values on the website that
belong to the same column. This is a desirable feature for our system as
users will not have to actively explore in order to discover which
values are available for scraping and how they are related to each
other. On the extension and repair front, Rousillon presents the web
scraping code generated by demonstration as an editable, high-level,
block-based language called Helena \citep{zotero-51}. While Helena can
be used to perform more complex editing tasks like adding control flow,
it presents a change in the model used for creation. Our system
maintains the model used for creation by allowing users to extend and
repair web scraping code via demonstration.

Vegemite \citep{lin2009} is a tool for end-user programming of mashups.
It has two interfaces: one for scraping values from a website and
another for creating scripts that operate on the scraped values. The web
scraping interface does not provide live feedback about the
generalization on hover but after a user clicks, the interface shows the
result of the system's generalization by highlighting the all matched
values. Furthermore, even though the interface also has a table, the
table is only populated with the scraped values after all the
demonstrations have been provided. The scripting interface utilizes
CoScripter \citep{leshed2008} which is used to record operations on the
scraped values for automation. For example, the scripting interface can
be used to demonstrate the task of copying an address in the table,
pasting it into a walk score calculator and pasting the result back into
the table. The script would then be generalized to all the rows and
re-run to fill in the remaining walk scores. CoScripter provides the
generated automation program as text-based commands, such as ``paste
address into `Walk Score' input,'' which can be edited after the program
is created via ``sloppy programming'' \citep{lin2009} techniques.
However, this editing does not extend to the web scraping interface used
for demonstrations.

Sifter \citep{huynh2006} is a tool that augments well structured
websites with advanced sorting and filtering functionality. Like
Wildcard, it uses web scraping to extract data from websites in order to
enable customizations (sorting and filtering). Unlike Wildcard, it does
not support adding annotations to websites and running computations on
the scraped data using a spreadsheet formula language. Both of these
significantly expand the types of customizations end-users can make to
websites. Sifter performs the web scraping automatically using a variety
of heuristics and solicits guidance from the user if this fails. While
automatic web scraping seems desirable, it is unclear how useful it is
if the goal is customization. Given a row with ten scrapable values, and
therefore ten columns, would a user prefer to simply demonstrate the
value for the single column they are interested in or un-demonstrate the
nine values they are not interested in? This is a question we can only
answer after performing a user study.

>>>>

This type of divide between tasks appears in other domains. In data
science, workflows revolve between cleaning and using data but this
often happens in different environments. The creators of Wrex
\citep{drosos2020}, an end-user programming-by-example system for data
wrangling, reported that ``although data scientists were aware of and
appreciated the productivity benefits of existing data wrangling tools,
having to leave their native notebook environment to perform wrangling
limited the usefulness of these tools.'' This was a major reason Wrex
was developed as an add-on to Jupyter notebooks, the environment in
which data scientists use their data. In web scraping, if a user comes
across an omission while working with data scraped from a website, they
need to switch from the environment in which they are using the data to
the environment in which they created their scraping code in order to
edit and re-run it. This can be seen in many end-user web scraping
systems like Rousillon \citep{chasins2018} and commercial tools like
import.io \citep{zotero-77}, dexi.io \citep{dexi.io}, Octoparse
\citep{zotero-83} and ParseHub \citep{zotero-86}. In web customization,
the creators of Vegemite \citep{lin2009}, a system for end-user
programming of mashups, reported that participants of its user study
thought ``it was confusing to use one technique to create the initial
table, and another technique to add information to a new column.'' This
hints at the need for both a unified environment and a unified workflow.

@@

Many end-user web scraping and macro systems allow users to
\emph{create} programs by demonstration but do not offer a way to
\emph{edit} them by demonstration. In Rousillon \citep{chasins2018}, a
web scraping program created by demonstration can only be edited through
a high-level, block-based programming language called Helena
\citep{zotero-51}. Helena supports adding control flow logic
(conditional execution, wait times etc) which is invaluable for
automating access to websites. However, it does not support extending
the web scraping code to add new columns after the demonstration or
repairing it to provide new selectors if the website changes. In
Vegemite \citep{lin2009}, a web automation program created through
demonstration can only be edited by editing the text-based
representation of the automtation. In fact, only the automation script
that works on the scraped website data can be edited. If a user needs to
add a new column or repair an exisiting one in the table, they need to
re-demonstrate the columns and then re-run the automation script.

@@

Rousillon \citep{chasins2018} is a tool that enables end-users to scrape
distributed, hierarchical web data. Its interface does not provide
\emph{full} live feedback about its generalizations or the values to be
scrapped until all the demonstrations have been provided and the
generated program has been run. If run on a website it has encountered
before, Rousillon makes all the previously determined generalizations
visible to the user by color-coding the values on the website that
belong to the same column. This is a desirable feature for our system as
users will not have to actively explore in order to discover which
values are available for scraping and how they are related to each
other. On the extension and repair front, Rousillon presents the web
scraping code generated by demonstration as an editable, high-level,
block-based language called Helena \citep{zotero-51}. While Helena can
be used to perform more complex editing tasks like adding control flow,
it does not support adding or repairing columns after the demonstrations
and presents a change in the model used for creation. Our system
maintains the model used for creation by allowing users to extend and
repair web scraping code via demonstration.

Vegemite \citep{lin2009} is a tool for end-user programming of mashups.
It has two interfaces: one for scraping values from a website and
another for creating scripts that operate on the scraped values. The web
scraping interface does not provide live feedback about the
generalization on hover but after a user clicks a value, the interface
shows the result of the system's generalization by highlighting the all
matched values. Furthermore, even though the interface also has a table,
the table is only populated with the scraped values after all the
demonstrations have been provided. The scripting interface utilizes
CoScripter \citep{leshed2008} which is used to record operations on the
scraped values for automation. For example, the scripting interface can
be used to demonstrate the task of copying an address in the table,
pasting it into a walk score calculator and pasting the result back into
the table. The script would then be generalized to all the rows and
re-run to fill in the remaining walk scores. CoScripter provides the
generated automation program as text-based commands, such as ``paste
address into `Walk Score' input,'' which can be edited after the program
is created via ``sloppy programming'' \citep{lin2009} techniques.
However, this editing does not extend to the web scraping interface used
for demonstrations and presents a change in the model used for creation.

Sifter \citep{huynh2006} is a tool that augments well structured
websites with advanced sorting and filtering functionality. Like
Wildcard, it uses web scraping to extract data from websites in order to
enable customizations (sorting and filtering). Unlike Wildcard, it does
not support adding annotations to websites and running computations on
the scraped data using a spreadsheet formula language. Both of these
significantly expand the types of customizations end-users can make to
websites. Sifter performs the web scraping automatically using a variety
of heuristics and solicits guidance from the user if this fails. While
automatic web scraping seems desirable, it is unclear how useful it is
if the goal is customization. Given a row with ten scrapable values, and
therefore ten columns, would a user prefer to simply demonstrate the
value for the single column they are interested in or un-demonstrate the
nine values they are not interested in? This automatic web scraping
aproach can be also be seen in tools like import.io \citep{zotero-77} so
it is certainly worth evaluating as part of a user study.
